### 2016-08-31 doc/publications/plos16/plos16.tex
changes to plos16.tex

  \item Chen (2012)  (done)
  \item VSURF and  varSelRF, (doee) recursive feature (forwards backwards) using variable importance
  \item ranger package
  \item  r2VIM: A new variable selection method for random forests in
    genome-wide association studies
  \item CloudForest: A Scalable and Efficient Random Forest Implementation for Biological Data
  \item \cite{Tuv.et.al.2009} feature selection via adding permuted variables. Do we want to consider this? (no, leave it for now)
  \end{itemize}
\item other things to do
  \begin{itemize}
  \item what is the problem with bagging? Do we need to redo the thousand genome stuff?
  \end{itemize}
\end{itemize}

@@

The digital revolution is seeing a dramatic increase in data collected about every aspect of 
life~\cite{Loebbecke2015}.  These data sets are not only growing vertically by capturing more and more events but also
horizontally by capturing more information about these events.  The challenge of big and `wide' data is especially
pronounced in the health space where whole genome sequence (WGS) technology enabled researchers to interrogate all 3
billion base pairs of the human genome.  While a large fraction of this data is identical between individuals,
identifying the relevant and disease specific differences is the focus of complex trait analysis [citation].

>>>>

  \item Chen (2012)  (done)
  \item VSURF and  varSelRF, (done) recursive feature (forwards backwards) using variable importance
  \item \cite{Wright.and.Ziegle.2016} ranger package (doing it!)
  \item  r2VIM: A new variable selection method for random forests in
    genome-wide association studies
  \item CloudForest: A Scalable and Efficient Random Forest
    Implementation for Biological Data
   Ensembles of decision trees in go/golang   --  do we need to look
   at this? 
  \item \cite{Tuv.et.al.2009} feature selection via adding permuted variables. Do we want to consider this? (no, leave it for now)
  \end{itemize}
\item other things to do
  \begin{itemize}
  \item what is the problem with bagging? Do we need to redo the thousand genome stuff?
  \end{itemize}
\end{itemize}

@@

The digital revolution is seeing a dramatic increase in data collected about every aspect of 
life~\cite{Loebbecke2015}.  These data sets are not only growing vertically by capturing more and more events but also
horizontally by capturing more information about these events.  The challenge of big and `wide' data is especially
pronounced in the health space where whole genome sequence (WGS) technology enabled researchers to interrogate all 3
billion basepairs of the human genome.  While a large fraction of this data is identical between individuals, \marginpar{base-pairs}
identifying the relevant and disease specific differences is the focus of complex trait analysis [citation].
